\documentclass[11pt]{resume}

%% \addtolength{\oddsidemargin}{-.25in}
%% \addtolength{\evensidemargin}{-.25in}
%% \addtolength{\textwidth}{0.5in}

\author{Seth P. Sevier}
\email{seth.sevier@gmail.com}
\streetaddress{11 Cherrywood Lane}
\citystatezip{Rome, NY 13440}
\phone{(315) 439-4598}

\begin{document}

\maketitle
\smallskip

\section{Experience}
\affiliation[Software Engineer, Associate]{Technergetics, Utica, NY}{June, 2018--Present}
\begin{itemize}
\item Site Reliability Engineering utilizing Pivotal Cloud Foundry, Amazon Web Services, and Kubernetes.  Managing and developing Infrastructure as Code across multiple security enclaves.  Full-stack web development using Python and MySQL.
\item Java development, testing, and documentation for small-scale computer systems.
\item Android application development using Java and Kotlin.
\end{itemize}

\bigaffiliation[Cyber Systems Operator, Staff Sergeant]{NY Air National Guard, Hancock Field, Syracuse, NY}{June, 2015--June, 2020}{174th Operations Support Squadron}
\begin{itemize}
\item Provide core Information Technology services to customers by configuring, installing, managing operating systems, and server applications.  Additionally managing system accounts, implementing security updates, performing vulnerability patching, and supporting warfare operations within strictly controled security parameters.
% \item Discovered and responded to a server room emergency cooling failure preventing mission outage.
% \item Successfully set up two Cisco Assured Compliance Assessment Solution servers with no prior knowledge of how ACAS systems work and with minimal documentation.
\item Airman of the Year for the 174th Attack Wing, 2017.
% \item Volunteer member of NY State Disaster Initial Recovery Force.
% \item Volunteer Physical Training Leader
\end{itemize}

\section{Education}
\affiliation[B.S. Degree in Network and Computer Security, Minor in Computer Science]{State University of NY Polytechnic Institute -- \normalfont Utica, NY}{May, 2018}
\begin{itemize}
\item Outstanding Student in the B.S. Program in Network and Computer Security Award, 2018
\item 3.8 GPA, made President's List every semester.
\item Publication: S. Sevier and A. Tekeoglu, "Analyzing the Security of Bluetooth Low Energy," 2019 International Conference on Electronics, Information, and Communication (ICEIC)
% \item Member of the Network and Computer Security Club.
\end{itemize}

\affiliation[A.A.S. Degree in Information Systems Technology]{Community College of the Air Force}{December, 2019}

\affiliation[\normalfont Keesler Air Force Base, Biloxi, MS]{U.S. Air Force Cyber Systems Operations Technical Training School}{December, 2015}

\affiliation[\normalfont Lackland Air Force Base, San Antonio, TX]{U.S. Air Force Basic Military Training}{August, 2015}

\affiliation[\normalfont Central Square, NY]{Paul V. Moore High School}{June, 2014}
\begin{itemize}
\item Received an Advanced Regents Diploma with Honors, GPA of 94
%\item Inducted into the National Honor Society as a Junior
\end{itemize}

%% \section{Certifications and Clearance}
%% \begin{itemize}
%% \item Security clearance available upon request
%% \item Active CompTIA Security+ Certification
%% \end{itemize}

\section{Certifications and Proficiencies}
\begin{itemize}
\item Active Security+ Certification
% \item Hobbyist Linux enthusiast of 11 years.
\item Experience with programming and scripting in BASH, Python, Haskell, Java, C, and Kotlin.
\end{itemize}

\end{document}
